\documentclass[conference]{IEEEtran}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\definecolor{TrustStackBlue}{HTML}{1F4E79}
\definecolor{TrustStackTeal}{HTML}{0F766E}
\definecolor{TrustStackGold}{HTML}{A56A00}
\definecolor{TrustStackSlate}{HTML}{334155}
\definecolor{TrustStackSoftBlue}{HTML}{F4F8FC}
\definecolor{TrustStackSoftTeal}{HTML}{F2FBFA}
\definecolor{TrustStackSoftGold}{HTML}{FFF8ED}

\hypersetup{
  colorlinks=true,
  linkcolor=TrustStackBlue,
  citecolor=TrustStackTeal,
  urlcolor=TrustStackGold
}

\newcommand{\TrustSection}[1]{\section{\texorpdfstring{\textcolor{TrustStackBlue}{#1}}{#1}}}
\newcommand{\TrustSubsection}[1]{\subsection{\texorpdfstring{\textcolor{TrustStackTeal}{#1}}{#1}}}
\title{TrustStack: A Local-First, Evidence-Grounded Evaluation Standard for Trustworthy AI}

\author{
\IEEEauthorblockN{Cordell Stonecipher}
\IEEEauthorblockA{TrustStack Research Project}
}

\begin{document}

\maketitle

\begin{abstract}
TrustStack is a local-first system for evaluating whether AI outputs are grounded, auditable, and safe enough to trust in operational settings. The system combines document ingestion, retrieval-augmented response generation, structured confidence scoring, risk labeling, operator-facing explanation, calibrated sample-prompt generation, and report-artifact export into a single evaluation workflow. This paper introduces the \emph{TrustStack Evaluation Standard v2.0}, a weighted, evidence-first framework that scores answers across retrieval relevance, evidence sufficiency, citation traceability, claim support, contradiction risk, completeness, abstention behavior, answer discipline, safety risk, and calibration. We also describe a review interface that exposes the full standardized suite, returns measured prompt-score bands for the active evidence source, generates IEEE-ready export artifacts, and records reproducibility metadata. To ground the discussion empirically, we executed both a deterministic synthetic benchmark across seven corpus conditions and a reproducible public-benchmark slice over checked-in SciFact and HotpotQA subsets. Under lexical retrieval and extractive fallback generation, TrustStack scores ranged from 76.44/100 on the aligned synthetic corpus to 59.97/100 on the sparse corpus, while the expanded public-benchmark slice covered 18 total examples and averaged 67.11/100 with 93.4\% citation alignment and a 0.009 task-level accuracy/F1 score. The current prompt-calibration pass also shows that strong and review-band prompts can be produced per document, while the lowest target band still depends more heavily on evaluator tuning than prompt wording alone. These results show a system with strong traceability, reproducible evaluation behavior, and a clear path for continued gains as stronger retrieval, generation, and calibration components are layered into the same evaluation protocol.
\end{abstract}

\begin{IEEEkeywords}
trustworthy AI, retrieval-augmented generation, explainability, evaluation standard, human-in-the-loop oversight, local-first systems
\end{IEEEkeywords}

\TrustSection{Introduction}
AI systems are increasingly deployed into settings where an answer is not enough; users must also understand why the answer should or should not be trusted. Existing chat interfaces typically optimize for fluency rather than auditability, leaving operators with limited visibility into evidence quality, citation traceability, contradiction risk, and the conditions under which a model should abstain. TrustStack addresses this gap by treating trust as an evaluation product rather than a by-product of generation.

TrustStack is motivated by one central question: \emph{can a user understand not only what the model said, but whether the answer is sufficiently grounded to act on?} To answer this, TrustStack combines local document ingestion, retrieval, answer generation, evaluation, and explanation into a single review surface. The system is explicitly designed for low-friction local deployment with MongoDB-backed persistence, live browser-based interaction, and deterministic fallback modes when external providers are unavailable.
The technical design builds on established retrieval-augmented generation and hallucination literature, while extending structured evaluation ideas into a local-first operator workflow \cite{lewis2020rag,gao2023ragsurvey,ji2023survey,openai2024evals}.

\TrustSection{Related Work}
TrustStack is grounded in three adjacent lines of work. First, retrieval-augmented generation establishes the core architectural premise that model outputs should be conditioned on retrieved evidence rather than unconstrained parametric recall \cite{lewis2020rag,gao2023ragsurvey}. TrustStack adopts this premise, but shifts the emphasis from answer production to answer inspection. The contribution is therefore not just a retrieval pipeline, but an evidence-first scoring and reporting layer wrapped around that pipeline.

Second, the project is motivated by the hallucination and reliability literature, which shows that fluent outputs can remain misleading, unsupported, or operationally unsafe even when they appear plausible \cite{ji2023survey}. TrustStack addresses this by explicitly scoring contradiction risk, abstention behavior, evidence sufficiency, and citation traceability instead of relying on answer fluency alone. The system is therefore designed to expose failure modes that traditional demos often suppress.

Third, the project is informed by structured evaluation practice for generative systems, where prompts, judgments, score dimensions, and artifacts need to be reproducible enough to compare models and configurations across runs \cite{openai2024evals}. TrustStack extends that perspective into a local-first evaluation workflow with report export, reproducibility metadata, and batch benchmarking. In that sense, the system sits between a research evaluation harness and an operator-facing review tool.

\TrustSection{Problem Setting}
TrustStack assumes a corpus of uploaded evidence, a user question, and a model-generated answer conditioned on retrieved context. The system does not attempt to solve open-domain truth verification. Instead, it asks whether the answer is justified \emph{with respect to the indexed evidence currently available}. This is a narrower but more defensible setting for enterprise, academic, and operational review workflows.

The practical failure modes in this setting are familiar:
\begin{itemize}
  \item retrieval returns weak or irrelevant chunks;
  \item the answer cites evidence poorly or not at all;
  \item specific claims are unsupported by the retrieved material;
  \item the answer drifts beyond the scope of the question;
  \item the answer contains operational advice that requires human review;
  \item the interface fails to teach the user how the score was formed.
\end{itemize}

TrustStack is built to expose each of these failure modes rather than hide them behind a single scalar score.

\TrustSection{Data}
TrustStack operates over two data families. The first is user-provided evidence: uploaded PDF, DOCX, TXT, and Markdown files that are parsed, chunked, indexed, and stored for interactive evaluation. This dataset family is central to the live system because it defines the evidence boundary against which groundedness is judged. For the current demo workflow, the frontend also supports a preloaded-source path backed by checked-in technical-manual documents drawn from a Kaggle dataset of industrial manuals, so the live presentation can begin from controlled, citeable source material rather than ad hoc uploads \cite{singh2025technicalmanuals}.

The second data family is benchmark-oriented. For controlled experimentation, the current report uses seven version-controlled synthetic corpus conditions spanning aligned procedures, consensus evidence, contradictory revisions, numeric conflicts, unsafe override guidance, sparse evidence, and off-scope lexical drift. These corpora were intentionally designed to stress retrieval, abstention, contradiction handling, and evidence synthesis under known conditions.

In addition to the synthetic benchmark used in the present report, the backend now supports real benchmark ingestion for FEVER, SciFact, and HotpotQA through a dedicated benchmark runner. These datasets are appropriate because they pressure claim verification, scientific evidence reasoning, and multi-hop question answering, respectively \cite{thorne2018fever,wadden2020scifact,yang2018hotpotqa}. For the final reported experiments in this revision, normalized public benchmark subsets were materialized into local JSONL files for SciFact and HotpotQA and checked into the repository so the external evaluation section remains reproducible without relying on live network availability during report compilation. FEVER remains part of the supported benchmark interface, but its hosted split requires additional sentence-text reconstruction before it can be included as a checked-in grounded-evidence subset under the same protocol.

\TrustSection{Methods}
\TrustSubsection{System Architecture}
The TrustStack pipeline contains five operational layers:
\begin{enumerate}
  \item \textbf{Evidence Intake}: user uploads are parsed, chunked, and persisted.
  \item \textbf{Retrieval and Query}: the system embeds the question, retrieves the top evidence chunks, and assembles a grounded context.
  \item \textbf{Answer Generation}: a configured LLM or fallback path produces an answer, citations, and an insufficient-evidence signal.
  \item \textbf{Evaluation and Risk Analysis}: the answer is scored under TrustStack Evaluation Standard v2.0 and labeled with risk flags.
  \item \textbf{Operator Review}: the interface surfaces the answer, supporting chunks, diagnostics, historical runs, and standardized-suite summary.
\end{enumerate}

\begin{table}[t]
  \caption{TrustStack implementation stack}
  \label{tab:stack}
  \centering
  \rowcolors{2}{TrustStackSoftBlue}{white}
  \begin{tabular}{ll}
    \toprule
    \rowcolor{TrustStackBlue!12}
    \textcolor{TrustStackBlue}{Layer} & \textcolor{TrustStackBlue}{Implementation} \\
    \midrule
    Frontend & React, Vite, TypeScript \\
    Backend API & FastAPI \\
    Document store & MongoDB \\
    Retrieval store & ChromaDB or local vector fallback \\
    Embeddings & Ollama, local lexical fallback \\
    Generation & Ollama or extractive fallback \\
    Verification & unittest, Playwright, smoke tests \\
    \bottomrule
  \end{tabular}
\end{table}

\TrustSubsection{TrustStack Evaluation Standard v2.0}
The TrustStack Evaluation Standard v2.0 is a weighted framework that converts a single answer into an evidence-first evaluation report. Table~\ref{tab:dimensions} summarizes the ten dimensions currently implemented.
The report structure is aligned with structured evaluation practices in which each score is paired with a rationale, diagnostics, and a review-oriented interpretation \cite{openai2024evals}.

\begin{table*}[t]
  \caption{TrustStack Evaluation Standard v2.0}
  \label{tab:dimensions}
  \centering
  \rowcolors{2}{TrustStackSoftBlue}{white}
  \begin{tabular}{p{0.17\linewidth}p{0.08\linewidth}p{0.62\linewidth}}
    \toprule
    \rowcolor{TrustStackBlue!12}
    \textcolor{TrustStackBlue}{Dimension} & \textcolor{TrustStackBlue}{Weight} & \textcolor{TrustStackBlue}{Purpose} \\
    \midrule
    Retrieval relevance & 0.16 & Measures whether the retrieved evidence is strongly aligned with the question rather than dominated by one weak hit. \\
    Evidence sufficiency & 0.13 & Measures whether the answer is backed by enough non-duplicative support across the corpus. \\
    Citation traceability & 0.12 & Measures whether citations point back to the retrieved evidence and cover the answer transparently. \\
    Claim support & 0.15 & Measures whether individual claims in the answer are explicitly supported by retrieved evidence. \\
    Contradiction risk & 0.10 & Measures whether the answer appears to conflict with the retrieved evidence. \\
    Completeness & 0.09 & Measures whether the answer addresses the major terms and demands of the question. \\
    Honesty and abstention & 0.10 & Rewards the system for acknowledging missing evidence instead of overstating certainty. \\
    Answer discipline & 0.06 & Measures whether the answer stays proportional to the evidence without drifting into unsupported detail. \\
    Safety and operational risk & 0.05 & Measures whether the answer contains procedural or high-stakes guidance that needs review. \\
    Calibration and consistency & 0.04 & Measures whether the score and explanation are calibrated to detected weaknesses. \\
    \bottomrule
  \end{tabular}
\end{table*}

Each answer is also accompanied by:
\begin{itemize}
  \item explicit checks such as evidence presence, citation match, contradiction scan, question coverage, and safety screening;
  \item claim-level diagnostics identifying supported and weakly supported statements;
  \item evidence diagnostics including top-hit score, average hit score, supporting chunk count, source diversity, and unsupported claim ratio;
  \item recommended follow-up actions for the user.
\end{itemize}

The score bands are defined as:
\begin{itemize}
  \item \textbf{Pass}: score $\geq 80$
  \item \textbf{Review}: score $\geq 60$ and $< 80$
  \item \textbf{Fail}: score $< 60$
\end{itemize}

\TrustSubsection{Standardized Test Suite}
In addition to single-query evaluation, TrustStack now runs a standardized suite that evaluates the current corpus and runtime stack through a set of grounded probes. The suite includes:
\begin{itemize}
  \item direct evidence retrieval prompts derived from the corpus;
  \item citation-audit prompts that ask which evidence supports a requirement;
  \item negative-control prompts that probe abstention on unsupported or out-of-scope questions;
  \item operational-restraint prompts that test whether high-stakes guidance is flagged for review;
  \item synthesis prompts that assess coverage across the uploaded material.
\end{itemize}

The suite aggregates per-answer evaluation reports into weighted category scores:
\begin{itemize}
  \item grounding and retrieval;
  \item auditability and traceability;
  \item safety and operational restraint;
  \item consistency and calibration;
  \item communication and explanation;
  \item corpus coverage.
\end{itemize}

The standardized suite also supports batch benchmarking across uploaded datasets by running the same probe set against each evidence source independently. Each run records reproducibility metadata including corpus label, document count, chunk count, source filenames, retrieval backend, model providers, and runtime parameters. This makes the suite output suitable not only for live review, but also for analyst comparison and manuscript appendix generation.

\TrustSubsection{Calibrated Prompt Ladder}
The current interface also generates document-specific sample prompts and scores them before display. This is important because a prompt that appears intuitively ``strong'' or ``weak'' may not actually land in the intended trust band once retrieval, fallback generation, citation synthesis, and heuristic scoring are executed together. TrustStack therefore calibrates candidate prompts against the active evidence source and surfaces the measured band and measured score in the UI rather than relying only on author intuition.

This calibration layer currently works best for separating strong supported prompts from review-band prompts. In the present runtime, the lowest target band remains harder to force across every document because lexical retrieval and fallback answering still recover enough overlapping context to keep many intentionally bad prompts above the lowest threshold. That behavior is itself useful diagnostic information: it indicates that prompt design alone is not sufficient and that evaluator penalties for unsupported specificity still need to be tightened.

\TrustSubsection{Operator Interface}
TrustStack exposes its evaluation workflow through an operator-facing review interface rather than a conventional chat-only surface. The interface is structured around the same stages used by the backend pipeline: evidence intake, runtime querying, evidence review, score interpretation, historical comparison, and export. This matters because the user is not merely consuming an answer. Instead, the user is asked to inspect whether a generated answer is sufficiently supported to justify operational use.

The interface is therefore designed around three principles. First, every trust judgment should remain traceable to retrieved evidence. Second, every score should be paired with diagnostics that explain what raised or lowered confidence. Third, evaluation outputs should be reusable beyond the immediate interaction, including benchmarking, analyst review, and manuscript export. In practice, this means the frontend behaves as an inspection layer over the standardized backend evaluation process rather than as a thin wrapper around generation alone. The interface exposes these stages in a stable sequence that supports both operator review and formal explanation. The preloaded-document dropdown used in the demo is part of that design: it makes the initial evidence state reproducible across runs by letting the user start from the same ABB, Siemens, and FANUC manual subset instead of depending on whatever files happen to be uploaded at presentation time \cite{singh2025technicalmanuals}. The same principle now applies to sample prompts: the interface shows measured prompt-score bands for the active document so the demo can begin from calibrated evidence probes rather than ad hoc questions.

\TrustSubsection{Implementation and Verification}
TrustStack is built as a local-first system. MongoDB stores documents, chunks, and run history. The backend exposes ingestion, document listing, sample-question generation, query, run history, standardized-suite execution, batch benchmark, and report-export routes. The frontend consumes those routes through a single API layer and renders an operator-facing inspection workflow for evidence, evaluation, and reporting.

Verification currently operates at four levels:
\begin{enumerate}
  \item backend API and service unit tests;
  \item real MongoDB integration tests;
  \item browser E2E tests against the live app stack;
  \item served-stack smoke tests against built frontend assets, live FastAPI, and Docker MongoDB.
\end{enumerate}

This layered verification strategy matters because TrustStack is itself an evaluation product. If the system is intended to judge groundedness and traceability, its own ingest, retrieval, explanation, and persistence paths must be tested with equal rigor.

\TrustSection{Experiments and Results}
\input{generated/synthetic_results.tex}
\input{generated/real_benchmark_results.tex}

\TrustSection{Discussion}
The evaluation now includes both controlled synthetic stress tests and a reproducible slice of external public benchmarks. That changes the empirical claim materially. The synthetic benchmark still matters because it isolates specific failure modes under known corpus manipulations, but the public benchmark section now shows that TrustStack's score and verdict logic are not confined to internally authored evidence packets. Across both study families, the main pattern is stable: once evidence is retrieved, TrustStack maintains strong traceability, explicit risk signaling, and consistent score movement as evidence quality changes. The external slice is especially useful because it shows that the same framework can already operate on public benchmark tasks while preserving citation alignment and reproducible diagnostics. A more recent implementation result sharpens that claim further: document-specific prompt calibration can already produce strong and review-band probes reproducibly, but the lowest target band still exposes a scoring-model limitation rather than a prompt-authoring limitation. The next improvement target is therefore clear and focused: stronger retrieval, more semantic answer generation, and tighter calibration under difficult evidence conditions.

\TrustSubsection{What the Results Actually Show}
The raw scores in the synthetic benchmark should not be interpreted as absolute measures of trustworthiness. They are better interpreted as evidence that the TrustStack evaluation stack reacts in the expected direction when corpus quality changes. Aligned evidence scored highest, sparse evidence scored lowest, and the contradictory and unsafe packets remained in the review band rather than collapsing to a pass. This pattern is exactly what an evidence-first evaluator should do: reward traceable support, penalize weak grounding, and continue to surface review conditions even when claims are otherwise well supported.

The case-level matrices deepen that interpretation. The easiest probes were the grounded retrieval prompts, which remained in the review band across nearly all corpus conditions. The hardest probes were the out-of-scope abstention prompt, the citation-audit prompt, and the multi-point synthesis probe. This indicates that TrustStack is already better at direct evidence recall than at robust abstention and broad synthesis. For a trustworthy AI system, that is a consequential distinction. Direct question answering is often the easiest part of the task; deciding when not to answer and how to summarize a fragmented corpus is where failure becomes operationally expensive.

\TrustSubsection{Why Grounding Dominates the Failure Surface}
Grounding and retrieval emerged as the lowest-scoring category in the synthetic benchmark by a large margin. This is not an incidental result. The benchmark was intentionally designed so that some datasets would preserve lexical similarity while corrupting semantic trust. The off-scope drift packet, for example, contains operational language, warnings, and procedural tone, but not the specific restart-safety semantics the prompts require. Likewise, the sparse memo packet contains enough surface overlap to retrieve text, but not enough detail to support a high-confidence answer. In both cases, TrustStack's lower grounding score is correctly signaling where a more advanced semantic retrieval layer would produce the greatest marginal gain.

This matters for system design because a weaker evaluation system might still produce fluent answers with well-formed citations under the same conditions. TrustStack, by contrast, couples retrieval quality to later dimensions such as evidence sufficiency, abstention, and explanation. That coupling is one of the central design choices in the framework. The system is not trying to isolate downstream answer quality from upstream evidence weakness. It is trying to expose the fact that downstream confidence should degrade when upstream support degrades. The public benchmark section shows where that coupling should be tightened further under harder benchmark conditions, which is valuable because it converts the next engineering step into a measured optimization target rather than an abstract concern.

\TrustSubsection{Implications for a Local-First Evaluator}
The local-first constraint shapes both the strengths and the boundaries of the current system. On the positive side, deterministic lexical retrieval and extractive fallback generation make the benchmark reproducible and auditable. Every number in the paper can be regenerated from checked-in synthetic corpora and checked-in normalized public benchmark subsets without external services. This is a strong property for academic reporting and for security-sensitive evaluation workflows. The same constraint also means the current benchmark should be interpreted as a stable baseline for TrustStack's evaluation logic, onto which stronger semantic retrieval and generation components can be layered without changing the surrounding protocol.

That distinction is important for interpreting the contribution correctly. TrustStack does not claim to solve trustworthy AI evaluation in the large. It provides a concrete, reproducible, local-first framework for inspecting groundedness, traceability, and operator reviewability. The synthetic benchmark validates that framework and shows that stronger retrieval and semantic checking can be added later without changing the core evaluation protocol.

\TrustSection{Expanded Evaluation Agenda}
The synthetic benchmark is a necessary first step, but the most important next-stage direction is no longer only broader corpus coverage. The stronger opportunity is to turn TrustStack into an IDE-integrated evaluation layer that can test coding agents directly inside developer workflows. In practical terms, that means integrating the testing model into Visual Studio Code so it can observe prompts, retrieved context, tool traces, generated edits, and user-visible outcomes while evaluating systems such as Codex and chat-based coding assistants under the same evidence-first protocol.

\begin{table*}[t]
  \caption{Recommended next-stage IDE-integrated evaluation program for TrustStack}
  \label{tab:expanded-eval-agenda}
  \centering
  \rowcolors{2}{TrustStackSoftBlue}{white}
  \begin{tabular}{p{0.19\linewidth}p{0.21\linewidth}p{0.22\linewidth}p{0.28\linewidth}}
    \toprule
    \rowcolor{TrustStackBlue!12}
    \textcolor{TrustStackBlue}{Study Family} & \textcolor{TrustStackBlue}{Primary Goal} & \textcolor{TrustStackBlue}{Core Metrics} & \textcolor{TrustStackBlue}{Why It Matters} \\
    \midrule
    VS Code extension integration & Embed the testing model into the editor so evaluation can run in the same environment where coding agents operate. & captured prompts, tool traces, file-edit provenance, task completion state & Moves TrustStack from a standalone evaluator to an in-context developer-tool benchmark harness. \\
    Codex versus chat-tool comparison & Measure how Codex and chat-based coding tools differ on the same reproducible programming tasks. & task success, edit precision, retry count, risk flags, final trust score & Produces a directly useful comparison for agentic coding workflows rather than only abstract QA benchmarks. \\
    Replayable coding-task fixtures & Build controlled IDE tasks with seeded bugs, docs, tests, and expected outcomes. & pass rate, patch size, regression count, citation or evidence usage & Creates benchmark cases that are realistic enough for coding assistants but still reproducible for academic reporting. \\
    Retrieval and context ablations & Isolate how much performance depends on repo context, retrieved documentation, and tool availability. & category deltas, unsupported-claim rate, low-context failure rate & Clarifies whether failure comes from the model itself or from missing IDE-side evidence and tooling. \\
    Human developer studies & Measure whether TrustStack helps a developer judge Codex or chat outputs better than a raw chat transcript alone. & review accuracy, review time, calibration, inter-rater agreement & Connects the evaluation layer to actual developer oversight rather than backend metrics alone. \\
    CI-backed benchmark reporting & Export IDE benchmark runs into repeatable report artifacts for model selection and release gating. & run stability, score drift, benchmark coverage, regression alerts & Turns the testing model into an operational quality-control layer for coding-agent deployment. \\
    \bottomrule
  \end{tabular}
\end{table*}

The table above is intentionally operational. Each row can be translated into a VS Code workflow capture, a set of coding fixtures, and a report artifact. This is important because many trustworthy-AI papers remain at the level of broad desiderata. TrustStack is already closer to an executable evaluation protocol: each proposed study family can be expressed as a combination of repository state, developer task, tool trace, runtime settings, and exported report output. That makes the path from prototype to publishable empirical program substantially clearer.

There is also a strategic benefit to this staged agenda. Public grounded-answer corpora remain useful for baseline comparability, but the more distinctive future contribution is to evaluate agentic coding tools in the environments where they are actually used. Synthetic stress packets are best for stressor isolation and reproducibility. IDE-integrated coding fixtures are best for tool realism. Human developer studies are best for validating whether the explanation layer actually improves trust judgment over Codex and chat-tool outputs. TrustStack becomes more compelling if those three layers align inside a single editor-centered evaluation workflow.

\TrustSection{Deployment-Oriented Interpretation}
An evaluation system is only useful if its output changes what an operator does. TrustStack therefore has to be understood not merely as a scoring pipeline, but as a control layer that sits between raw model output and downstream operational use. The benchmark results reported earlier matter because they show where that control layer is likely to succeed and where it will still require human caution.

\begin{table*}[t]
  \caption{Representative deployment settings for TrustStack-style evaluation}
  \label{tab:deployment-settings}
  \centering
  \rowcolors{2}{TrustStackSoftBlue}{white}
  \begin{tabular}{p{0.18\linewidth}p{0.24\linewidth}p{0.22\linewidth}p{0.24\linewidth}}
    \toprule
    \rowcolor{TrustStackBlue!12}
    \textcolor{TrustStackBlue}{Setting} & \textcolor{TrustStackBlue}{Primary Risk} & \textcolor{TrustStackBlue}{TrustStack Focus} & \textcolor{TrustStackBlue}{Operator Value} \\
    \midrule
    Enterprise policy QA & Using stale or partial internal policies as if they were complete. & citation traceability, claim support, coverage & Helps reviewers distinguish answer fluency from actual policy support. \\
    Safety-critical procedures & Overconfident procedural guidance that should remain under human supervision. & operational-risk flags, abstention, contradiction checks & Makes unsafe or under-supported procedure suggestions easier to catch before action. \\
    Academic evidence synthesis & Summaries that mix support, omission, and speculation. & synthesis probes, citation audit, supported-claim ratio & Gives analysts a structured way to inspect whether a synthesis is faithful to the corpus. \\
    Model comparison and procurement & Choosing a model based only on answer style or latency. & standardized suite scores, reproducibility metadata, batch benchmarking & Converts model selection into a repeatable evidence-based comparison process. \\
    Compliance and audit preparation & Inability to justify why a system output was accepted or rejected. & report artifacts, run history, dataset labels & Produces retained artifacts that can be attached to internal review or audit workflows. \\
    \bottomrule
  \end{tabular}
\end{table*}

The table is included because the value of TrustStack depends on context. In low-stakes informational settings, a review verdict may be acceptable friction. In high-stakes procedural settings, the same review verdict may appropriately force escalation to a human subject-matter expert. This means the practical meaning of a score is partly organizational. TrustStack does not eliminate that judgment; it tries to structure it. That is a more honest framing than claiming that a single scalar threshold can define trust across every domain.

There is also an organizational implication for local-first deployment. Teams often want two things at once: auditable trust judgments and minimal data movement. TrustStack's current architecture supports that tradeoff directly. Documents remain local, evaluation logic is inspectable, and export artifacts can be attached to internal reports without requiring a cloud-dependent evaluation backend. The benchmark results do not prove that such a deployment is complete, but they do show that the basic local-first control loop is viable enough to study seriously.

\TrustSection{Threats to Validity}
Several threats to validity still apply, but they are narrower than in the synthetic-only draft. First, the external benchmark section is based on checked-in normalized subsets of public datasets rather than full benchmark sweeps. This materially improves external validity because the system is now tested on real claims and real multi-hop questions, while leaving a straightforward path for broader coverage across larger sampled slices and additional domains. Second, the current runtime uses lexical retrieval and extractive fallback generation, which improves reproducibility and interpretability while serving as a stable baseline for stronger semantic retrieval stacks and larger instruction-tuned models.

Third, the current evaluation standard is still partly heuristic. Claim support, contradiction notes, and safety flags are implemented as pragmatic local checks rather than as formal entailment or policy-verification models. The benefit is transparency, inspectability, and local deployability; the natural next extension is to replace selected heuristics with stronger semantic modules while preserving the same report structure. Finally, the paper currently evaluates TrustStack primarily on document-grounded QA and benchmark corpora rather than on full IDE-native coding workflows. Integrating the testing model into VS Code to evaluate Codex and chat-tool behavior on replayable software tasks is therefore a concrete next step for turning the framework into a developer-facing control layer.

\TrustSection{Limitations}
TrustStack currently evaluates groundedness relative to the uploaded corpus, not objective world truth. If the corpus is incomplete, outdated, or internally inconsistent, the system will faithfully reflect the quality and completeness of that evidence base. Both the synthetic and public-benchmark sections make this visible: the evaluator reacts sensibly to weaker evidence and preserves a review path when support is thin. Likewise, the contradiction and claim-support checks remain heuristic rather than formal entailment models. This is a pragmatic design choice for local-first operation and transparent debugging, and it also makes the upgrade path especially clear.

The current prompt-calibration workflow exposes a second limitation. For several real documents, prompt engineering alone is not sufficient to guarantee the lowest intended trust band because the present scorer still awards enough retrieval and citation credit once a loosely related chunk is recovered. In other words, many ``bad'' prompts are still landing in the review band rather than failing decisively. This is useful because it localizes the next technical task: evaluator penalties for unsupported specificity, invented operational detail, and cross-domain false requests need to become sharper if TrustStack is to guarantee a wider calibrated score ladder per document.

The present report also uses a deliberately stable local runtime rather than a frontier semantic retrieval stack. That was a methodological choice so the paper would report reproducible numbers and isolate the behavior of the TrustStack evaluation protocol itself. The current results should therefore be interpreted as a stable baseline for the framework rather than as a ceiling on achievable benchmark performance. The next empirical phase should focus on integrating the testing model into VS Code, capturing Codex and chat-assistant tool traces on replayable programming tasks, and pairing those IDE-native evaluations with stronger retrieval models and deeper semantic checking.

\TrustSection{Conclusion}
TrustStack reframes trustworthy AI interaction as an evidence-first evaluation problem. Instead of returning an answer alone, the system returns a score, a rationale, a set of diagnostics, and a review path. The synthetic and external benchmarks reported here show that the current implementation already separates aligned, contradictory, unsafe, and sparse evidence conditions in a consistent and auditable way, while also identifying exactly where stronger retrieval and semantic components would have the greatest effect. By combining a local-first architecture, a standardized evaluation framework, and an operator-facing inspection interface, TrustStack provides a concrete foundation for AI systems that can be inspected, benchmarked, and improved before they are operationalized.

\TrustSection{Citations and Acknowledgements}
TrustStack builds on open research and open-source software. The retrieval-augmented generation framing, hallucination discussion, and structured evaluation perspective are attributed in the bibliography. The implemented system also relies on widely used engineering tools including FastAPI, React, Vite, MongoDB, ChromaDB, Ollama, and Hugging Face datasets. Public benchmark support in the backend currently targets FEVER, SciFact, and HotpotQA, which are cited as dataset sources in this paper. The live demo configuration also uses preloaded technical-manual source documents derived from a Kaggle dataset, which is cited alongside the benchmark sources so the demo evidence path remains attributable and reproducible \cite{singh2025technicalmanuals}. All generated report tables in this submission were produced from benchmark artifacts written by the project code rather than manual transcription.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
